Final Report: Scenario 2 - MPX in the EU

### 2022-11-28 MS5.Rmd
Working on MS5

---
title: "Scenario 2 - MPX in the EU"
author: "Dawson Coblin and Jose Lazo"
date: '2022-11-21'
output: pdf_document
editor_options: 
  markdown: 
    wrap: 72
---

# Monkeypox (MPX) Infection Rates in the European Union

This report aims to prepare data to analyze and assess the impact of MPV
within\
each country of the EU, and understand how case rates may differ by
region and other various demographic factors. These findings will aid
the implementation and appropriate response to the epidemic to local
health departments.

### Legend of Tasks and Milestones

| Milestone   | Description of Section                                           |
|-----------------------|-------------------------------------------------|
| Milestone 1 | Group Agreement                                                  |
| Milestone 2 | Data-set Imported into R; Identify Key Data Elements and Types   |
| Milestone 3 | Clean Data-set Create Descriptive Statistics and Data Dictionary |
| Milestone 4 | Data Visualization                                               |

Milestone 3 Sub-sections:\
1.Sub-setting Rows and Columns as Needed- Clean individual Data Frames\
2.Summarizing Data and Creating New Vectors, Organize Vectors for Use\
3.Clean Variables and Combined Data-sets\
4.Descriptive Stats of EU Data and Data Dictionary

\newpage

### 1) Milestone 1: Group Agreement

Group R: Team Logistics Agreement

9/19/22

1.  Project option selection

Scenario 2: Monkeypox (MPX) infection rates in the European Union

2.  Create git repository

<https://github.com/dcoblin/251.git>

3.  Roles and responsibilities

```{=html}
<!-- -->
```
a.  Team's preferred communication method

WhatsApp

b.  Team's preferred meeting times and frequency

Weekends/Post 6 PM on weekdays

c.  Team's preferred method for tracking progress

Google docs

d.  Point person for contacting course facilitators with questions

Jose/Dawson

e.  Point person for submitting all milestones

Dawson/Jose

\newpage

### 2) Milestone 2: Data-set Imported into R; Identify Key Data Elements and Types

@@

```{r}
euro_mpx_cases <- read_csv("files/euro_mpx_cases.csv")
euro_census_stats <- read_csv("files/euro_census_stats.csv")
euro_pop_denominators <- read_csv("files/euro_pop_denominators.csv")
world_country_regions <- read_csv("files/world_country_regions.csv")
```

\newpage

## Milestone 3: 1. Sub-setting Rows and Columns as Needed- Clean individual Data Frames

### Data Frame Cleaning

```{r}
#Cleaning the cases df
euro_mpx_cases <- euro_mpx_cases %>%
  select( DateRep, CountryExp, CountryCode  ,ConfCases)

@@

head(euro_pop_denominators,3)

@@

head(euro_census_stats, 3)
```

\newpage

## Milestone 3: 2. Summarizing Data and Creating New Vectors, Organize Vectors for Use

```{r}
#We then assign counties with a region code in a new column a list "EU_region,"
#and include the country name and code
sr_northern_e<- c(
  "Denmark" , "Estonia", "Finland", "Iceland", "Ireland", "Latvia", "Lithuania",
  "Norway", "Sweden" , "DK" , "EE", "FI", "IE", "IS", "LT", "LU", "NO", "SE"
)
sr_western_e<- c(
  "Austria", "Belgium", "France", "Germany", "Luxembourg", "Netherlands" , 
  "DE", "AT" , "BE" , "FR", "LV", "NL"
)
sr_eastern_e<- c(
  "Bulgaria", "Czechia", "Hungary", "Poland", "Romania", "Slovakia", "BG", "CZ",
  "HU", "PL" , "RO", "SK"
)
sr_southern_e<- c(
  "Croatia", "Greece", "Italy", "Malta", "Portugal", "Slovenia", "Spain", "EL", 
  "ES", "HR", "IT", "MT", "PT", "SI"
)
sr_western_a<- c( 
  "Cyprus" , "CY"
)

@@

#We now add the EU_Region vector based on the country name.
euro_mpx_cases <- euro_mpx_cases %>% 
  mutate(EU_region = case_when(
    CountryCode %in% sr_eastern_e ~ "Eastern Europe",
    CountryCode %in% sr_northern_e ~ "Northern Europe",
    CountryCode %in% sr_southern_e ~ "Southern Europe",
    CountryCode %in% sr_western_e ~ "Western Europe",
    CountryCode %in% sr_western_a ~ "Western Asia"
    ))

head(euro_mpx_cases,3)
```

\newpage

## Milestone 3: 3. Clean Variables and Combined Data-sets

```{r}

@@

head(euro_mpx_cases,3)
```

\newpage

## Milestone 3: 4. Descriptive Stats of EU Data and Data Dictionary

### Descriptive stats:

We find that the census information for 7 of the 29 countries in the EU
are not available. These "0" values were replaced with "NA" to prevent
graphing issues.

### Region Data:

We see that the regions in EU include various numbers of countries, thus
having unequal populations. A useful metric to create a graph will be
the calculation of cases per 100,000. This will allow us to use 1
categorical variable (EU Region) to a quantitative variable (number of
confirmed cases)

We compiled the relevant confirmed case information per region in the
EU.

### The pertinent information per EU region is listed below:

@@

## Data Dictionary

```{r, echo=FALSE}
#Create the Data Dictionary

names <- names(euro_mpx_cases)
data_type <- sapply(euro_mpx_cases,class)
description <- c("Reporting time period with the floor month", #floor_month
                 "Abbreviation of Country", # CountryCode
                 "The current population of the country for 2022", # country_pop_2022
                 "Total confirmed MPX cases grouped by month", # cases_grouped_monthly
                 "The designated region the country is located", # EU_region
                 "Sum of the four months per country code", # sum_region_cases
                 "The Sum of population 0-1000", # 0-1000
                 "The Sum of population 1000-9999", # 1000-9999
                 "The Sum of population 10000-99999", # 10000-99999
                 "The Sum of population 100000-199999", # 100000-199999
                 "The Sum of population 200000-499999", # 200000-499999
                 "The Sum of population 500000-999999", # 500000-999999
                 "The Sum of population GE1000000" # GE1000000
)

data_dic <- as.data.frame(cbind(names, data_type, description)) %>% 
  select(-names)

kable(data_dic,
      col.names = c("Data Type", 
                    "Description"),
      caption = "Data Dictionary"
      ) %>%
  kable_styling(latex_options = "HOLD_position")
```

\newpage

### Milestone 4: Visualizations

```{r Population Density Demographic Table}
euro_census_stats1 <- read_csv("files/euro_census_stats.csv")

@@

Table_2a <- pivot_wider(euro_census_stats2a,
            names_from = EU_region,
            values_from = pop_density_count)

kable(Table_2a,
      col.names = c("Population Density", "Eastern Europe", "Northern Europe",
                    "Southern Europe","Western Asia","Western Europe"),
      caption = "Population Demographic (Population Density) per Region") %>%
  kable_styling(latex_options = "HOLD_position")
```
## Table 4

Table 4 illustrates the strata of individuals living within each region of the EU by the population density of that region.

\newpage

```{r Age Demographic Table}
euro_census_stats2b <- euro_census_stats1 %>%
  group_by(COUNTRY_CODE, AGE) %>%
  summarise(census_pop = sum(pop)) %>%
  rename(CountryCode = COUNTRY_CODE) %>% 
  mutate(EU_region = case_when(
    CountryCode %in% sr_eastern_e ~ "Eastern Europe",
    CountryCode %in% sr_northern_e ~ "Northern Europe",
    CountryCode %in% sr_southern_e ~ "Southern Europe",
    CountryCode %in% sr_western_e ~ "Western Europe",
    CountryCode %in% sr_western_a ~ "Western Asia"
    ))

@@

Table_2b <- pivot_wider(euro_census_stats2b,
            names_from = EU_region,
            values_from = pop_density_count)

@@

## Table 5

Table 5 summarizes the region demographics by age using data that provides information by region based on age in specific brackets.

\newpage

```{r}
euro_mpx_cases %>% 
  ggplot(., aes(x = floor_month, y = cases_grouped_monthly)) +
  geom_bar(aes(fill = EU_region), stat = "identity") +
  theme_minimal() +
  labs(title = "Monthly Cases of Monkeypox in Europe", 
       tag = "Figure 1",
       x = "Month (2022)", 
       y = "Monkeypox Cases") +
  theme(axis.title = element_text(size = 10),
        axis.text = element_text(size = 8),
        axis.ticks.x = element_blank(),
        plot.title = element_text(size = 14),
        legend.title = element_blank(),
        plot.tag.position = "bottomleft") 
```

### Bar Graph
In the bar graph (fig. 1) above we see the breakdown of monthly MPX infections in Europe between May and August of this year. The majority of cases occurred in Western Europe and Southern Europe as evidenced by the respectively colored purple and green regions in the bar graph. Over the course of 4 months, the total number of MPX cases by region were Western Asia = 4, Eastern Europe = 277, Northern Europe = 619, Southern Europe = 7958, and Western Europe = 8214

\newpage

```{r}
euro_mpx_cases <- inner_join(euro_mpx_cases, Table_1.1, by= "EU_region") %>%
  group_by(floor_month) %>%
  mutate(Total_Euro_cases_monthly = sum(cases_grouped_monthly)) %>%
  mutate(Total_euro_pop = sum(country_pop_2022)) 
graph1 <- euro_mpx_cases %>%
  select(floor_month, cases_grouped_monthly, EU_region, sum_region_cases.x, Total_region_pop,
         Total_Euro_cases_monthly, Total_euro_pop) %>%
  group_by(floor_month, EU_region) %>%
  mutate(region_monthly_cases = sum(cases_grouped_monthly)) %>% ungroup() %>%
  mutate("monthly_rate_region" = round((region_monthly_cases/Total_region_pop * 100000),2))
ggplot(data=graph1, aes(x=floor_month, y=monthly_rate_region, group= EU_region)) +
  geom_line(aes(color=EU_region)) +
  geom_point() +
  geom_label(label= graph1$monthly_rate_region, nudge_y = 0.1) +
  theme_minimal() +
  labs(title = "Rate of Monkeypox Infections", 
       tag = "Figure 2",
       x = "Month (2022)", 
       y = "Monkeypox Rate (per 100k)") +
    theme(axis.title = element_text(size = 10),
        axis.text = element_text(size = 8),
        axis.ticks.x = element_blank(),
        plot.title = element_text(size = 14),
        legend.title = element_blank(),
        plot.tag.position = "bottomleft") 
```

### Line Plot
As a follow up to the bar graph (fig. 1) above, we wanted to look at the rate of MPX infections per region. In the bar graph above, Western Europe had the greatest number of MPX infections however when we look at the rate of infections (fig. 2), we see that over the course of the 4 months, Southern Europe had the greatest rate of infection with a peak of 2.84 MPX cases per 100,000 people in the month of July.

\newpage

```{r}
euro_census_stats2 <- read_csv("files/euro_census_stats.csv")
euro_census_stats2 <- euro_census_stats2 %>%
  mutate(AGE = case_when(AGE %in% c("Y_LT15") ~ "Age < 15",
                                  AGE %in% c("Y15-29") ~ "Age 15-29",
                                  AGE %in% c("Y30-49") ~ "Age 30-49",
                                  AGE %in% c("Y50-64") ~ "Age 50-64",
                                  AGE %in% c("Y65-84") ~ "Age 65-84",
                                  AGE %in% c("Y_GE85") ~ "Age 85 and Older")) %>%
  filter(pop > 0) %>%
  select(COUNTRY_CODE, SEX, AGE, pop) %>%
  ungroup() %>%
  group_by(COUNTRY_CODE, SEX, AGE) %>%
  summarise("age_category_count" = sum(pop)) %>%
  ungroup() %>%
  group_by(COUNTRY_CODE) %>%
  mutate(total_pop = sum(age_category_count)) %>% ungroup()

@@

demo_data <- left_join(euro_census_stats2, euro_mpx_cases2, by = "COUNTRY_CODE") %>%
  drop_na(total_cases) %>%
   mutate(COUNTRY_CODE = case_when(COUNTRY_CODE %in% c("AT") ~ "Austria",
                                   COUNTRY_CODE %in% c("BE") ~ "Belgium",
                                   COUNTRY_CODE %in% c("BG") ~ "Bulgaria",
                                   COUNTRY_CODE %in% c("HR") ~ "Croatia",
                                   COUNTRY_CODE %in% c("CY") ~ "Cyprus",
                                   COUNTRY_CODE %in% c("CZ") ~ "Czechia",
                                   COUNTRY_CODE %in% c("EE") ~ "Estonia",
                                   COUNTRY_CODE %in% c("FI") ~ "Finland",
                                   COUNTRY_CODE %in% c("FR") ~ "France",
                                   COUNTRY_CODE %in% c("EL") ~ "Greece",
                                   COUNTRY_CODE %in% c("HU") ~ "Hungary",
                                   COUNTRY_CODE %in% c("IE") ~ "Ireland",
                                   COUNTRY_CODE %in% c("LV") ~ "Latvia",
                                   COUNTRY_CODE %in% c("LU") ~ "Luxembourg",
                                   COUNTRY_CODE %in% c("MT") ~ "Malta",
                                   COUNTRY_CODE %in% c("PL") ~ "Poland",
                                   COUNTRY_CODE %in% c("PT") ~ "Portugal",
                                   COUNTRY_CODE %in% c("RO") ~ "Romania",
                                   COUNTRY_CODE %in% c("SK") ~ "Slovakia",
                                   COUNTRY_CODE %in% c("SI") ~ "Slovenia")) %>%
  group_by(COUNTRY_CODE, SEX, AGE, total_cases, total_pop) %>%
  filter(total_cases > 100) %>%
  mutate('age_cat_pct' = round((age_category_count/total_pop*100),digits = 2)) %>%
  select(COUNTRY_CODE, SEX, AGE, total_cases, total_pop, age_cat_pct) %>%
  group_by(COUNTRY_CODE, AGE, total_cases) %>%
  summarise(age_cat_pct = sum(age_cat_pct)) %>%
  arrange(desc(AGE))

@@

### Stacked Bargraph Age Distribution

@@

>>>>

---
title: "Final Report: Scenario 2 - MPX in the EU"
author: "Dawson Coblin and Jose Lazo"
date: '2022-11-28'
output: pdf_document
editor_options: 
  markdown: 
    wrap: 72
---

# Problem Statement

As the world begins to recover from the effects of COVID, the threat of the monkeypox virus (MPX) has public health officials preparing for the worst. Throughout Europe, cases of MPX have begun to rise and it is imperative to understand the groups at highest risk. This report aims to prepare data to analyze and assess the impact of MPX
within each country of the EU, and understand how case rates may differ by region and other various demographic factors. These findings will aid the implementation and appropriate response to the epidemic to local
health departments. Our team hypothesizes that monkeypox will be prevalent among the very young and old as is common for many infectious diseases.

# Methods

Datasets with information on confirmed cases of monkeypox per country as well as census data from Europe were used to prepare this report. Countries were grouped by region based on world_country_region data set to describe the cases per region.

Within the euro_mpx_cases dataset, relevant fields include country, country code, and confirmed cases. A curated demographic dataset included information on age, sex, and number of people per strata.

@@

```{r, include=FALSE}
euro_mpx_cases <- read_csv("files/euro_mpx_cases.csv")
euro_census_stats <- read_csv("files/euro_census_stats.csv")
euro_pop_denominators <- read_csv("files/euro_pop_denominators.csv")
world_country_regions <- read_csv("files/world_country_regions.csv")
```

```{r, include=FALSE}
#Cleaning the cases df
euro_mpx_cases <- euro_mpx_cases %>%
  select( DateRep, CountryExp, CountryCode  ,ConfCases)

@@

@@

```{r, include=FALSE}
#We then assign counties with a region code in a new column a list "EU_region,"
#and include the country name and code
sr_northern_e<- c(
  "Denmark" , "Estonia", "Finland", "Iceland", "Ireland", "Latvia", "Lithuania",
  "Norway", "Sweden" , "DK" , "EE", "FI", "IE", "IS", "LT", "LU", "NO", "SE"
)
sr_western_e<- c(
  "Austria", "Belgium", "France", "Germany", "Luxembourg", "Netherlands" , 
  "DE", "AT" , "BE" , "FR", "LV", "NL"
)
sr_eastern_e<- c(
  "Bulgaria", "Czechia", "Hungary", "Poland", "Romania", "Slovakia", "BG", "CZ",
  "HU", "PL" , "RO", "SK"
)
sr_southern_e<- c(
  "Croatia", "Greece", "Italy", "Malta", "Portugal", "Slovenia", "Spain", "EL", 
  "ES", "HR", "IT", "MT", "PT", "SI"
)
sr_western_a<- c( 
  "Cyprus" , "CY"
)

@@

#We now add the EU_Region vector based on the country name.
euro_mpx_cases <- euro_mpx_cases %>% 
  mutate(EU_region = case_when(
    CountryCode %in% sr_eastern_e ~ "Eastern Europe",
    CountryCode %in% sr_northern_e ~ "Northern Europe",
    CountryCode %in% sr_southern_e ~ "Southern Europe",
    CountryCode %in% sr_western_e ~ "Western Europe",
    CountryCode %in% sr_western_a ~ "Western Asia"
    ))
```

@@

# Results

@@

In table 1, we see that the regions in EU include various numbers of countries, thus
having unequal populations. A useful metric to create a graph will be
the calculation of cases per 100,000. This will allow us to use 1
categorical variable (EU Region) to a quantitative variable (number of
confirmed cases). We compiled the relevant confirmed case information per region in the
EU.

```{r Population Density Demographic Setup, include=FALSE}
euro_census_stats1 <- read_csv("files/euro_census_stats.csv")

@@

Table_2a <- pivot_wider(euro_census_stats2a,
            names_from = EU_region,
            values_from = pop_density_count)
```

```{r Population Density Demographic Table, echo=FALSE}
kable(Table_2a,
      col.names = c("Population Density", "Eastern Europe", "Northern Europe",
                    "Southern Europe","Western Asia","Western Europe"),
      caption = "Population Demographic (Population Density) per Region") %>%
  kable_styling(latex_options = "HOLD_position")
```

Table 2 illustrates the strata of individuals living within each region of the EU by the population density of that region.

```{r Age Demographic Setup, include=FALSE}
euro_census_stats2b <- euro_census_stats1 %>%
  group_by(COUNTRY_CODE, AGE) %>%
  summarise(census_pop = sum(pop)) %>%
  rename(CountryCode = COUNTRY_CODE) %>% 
  mutate(EU_region = case_when(
    CountryCode %in% sr_eastern_e ~ "Eastern Europe",
    CountryCode %in% sr_northern_e ~ "Northern Europe",
    CountryCode %in% sr_southern_e ~ "Southern Europe",
    CountryCode %in% sr_western_e ~ "Western Europe",
    CountryCode %in% sr_western_a ~ "Western Asia"
    ))

@@

Table_2b <- pivot_wider(euro_census_stats2b,
            names_from = EU_region,
            values_from = pop_density_count)
```

```{r Age Demographic table, echo=FALSE}

@@

Table 3 summarizes the region demographics by age using data that provides information by region based on age in specific brackets.

```{r, echo=FALSE}
euro_mpx_cases %>% 
  ggplot(., aes(x = floor_month, y = cases_grouped_monthly)) +
  geom_bar(aes(fill = EU_region), stat = "identity") +
  theme_minimal() +
  labs(title = "Monthly Cases of Monkeypox in Europe", 
       tag = "Figure 1",
       x = "Month (2022)", 
       y = "Monkeypox Cases") +
  theme(axis.title = element_text(size = 10),
        axis.text = element_text(size = 8),
        axis.ticks.x = element_blank(),
        plot.title = element_text(size = 14),
        legend.title = element_blank(),
        plot.tag.position = "bottomleft") 
```

In the bar graph (fig. 1) above we see the breakdown of monthly MPX infections in Europe between May and August of this year. The majority of cases occurred in Western Europe and Southern Europe as evidenced by the respectively colored purple and green regions in the bar graph. Over the course of 4 months, the total number of MPX cases by region were Western Asia = 4, Eastern Europe = 277, Northern Europe = 619, Southern Europe = 7958, and Western Europe = 8214

```{r, echo=FALSE}
euro_mpx_cases <- inner_join(euro_mpx_cases, Table_1.1, by= "EU_region") %>%
  group_by(floor_month) %>%
  mutate(Total_Euro_cases_monthly = sum(cases_grouped_monthly)) %>%
  mutate(Total_euro_pop = sum(country_pop_2022)) 
graph1 <- euro_mpx_cases %>%
  select(floor_month, cases_grouped_monthly, EU_region, sum_region_cases.x, Total_region_pop,
         Total_Euro_cases_monthly, Total_euro_pop) %>%
  group_by(floor_month, EU_region) %>%
  mutate(region_monthly_cases = sum(cases_grouped_monthly)) %>% ungroup() %>%
  mutate("monthly_rate_region" = round((region_monthly_cases/Total_region_pop * 100000),2))
ggplot(data=graph1, aes(x=floor_month, y=monthly_rate_region, group= EU_region)) +
  geom_line(aes(color=EU_region)) +
  geom_point() +
  geom_label(label= graph1$monthly_rate_region, nudge_y = 0.1) +
  theme_minimal() +
  labs(title = "Rate of Monkeypox Infections", 
       tag = "Figure 2",
       x = "Month (2022)", 
       y = "Monkeypox Rate (per 100k)") +
    theme(axis.title = element_text(size = 10),
        axis.text = element_text(size = 8),
        axis.ticks.x = element_blank(),
        plot.title = element_text(size = 14),
        legend.title = element_blank(),
        plot.tag.position = "bottomleft") 
```

As a follow up to the bar graph (fig. 1) above, we wanted to look at the rate of MPX infections per region. In the bar graph above, Western Europe had the greatest number of MPX infections however when we look at the rate of infections (fig. 2), we see that over the course of the 4 months, Southern Europe had the greatest rate of infection with a peak of 2.84 MPX cases per 100,000 people in the month of July.

```{r, include=FALSE}
euro_census_stats2 <- read_csv("files/euro_census_stats.csv")
euro_census_stats2 <- euro_census_stats2 %>%
  mutate(AGE = case_when(AGE %in% c("Y_LT15") ~ "Age < 15",
                                  AGE %in% c("Y15-29") ~ "Age 15-29",
                                  AGE %in% c("Y30-49") ~ "Age 30-49",
                                  AGE %in% c("Y50-64") ~ "Age 50-64",
                                  AGE %in% c("Y65-84") ~ "Age 65-84",
                                  AGE %in% c("Y_GE85") ~ "Age 85 and Older")) %>%
  filter(pop > 0) %>%
  select(COUNTRY_CODE, SEX, AGE, pop) %>%
  ungroup() %>%
  group_by(COUNTRY_CODE, SEX, AGE) %>%
  summarise("age_category_count" = sum(pop)) %>%
  ungroup() %>%
  group_by(COUNTRY_CODE) %>%
  mutate(total_pop = sum(age_category_count)) %>% ungroup()

@@

demo_data <- left_join(euro_census_stats2, euro_mpx_cases2, by = "COUNTRY_CODE") %>%
  drop_na(total_cases) %>%
   mutate(COUNTRY_CODE = case_when(COUNTRY_CODE %in% c("AT") ~ "Austria",
                                   COUNTRY_CODE %in% c("BE") ~ "Belgium",
                                   COUNTRY_CODE %in% c("BG") ~ "Bulgaria",
                                   COUNTRY_CODE %in% c("HR") ~ "Croatia",
                                   COUNTRY_CODE %in% c("CY") ~ "Cyprus",
                                   COUNTRY_CODE %in% c("CZ") ~ "Czechia",
                                   COUNTRY_CODE %in% c("EE") ~ "Estonia",
                                   COUNTRY_CODE %in% c("FI") ~ "Finland",
                                   COUNTRY_CODE %in% c("FR") ~ "France",
                                   COUNTRY_CODE %in% c("EL") ~ "Greece",
                                   COUNTRY_CODE %in% c("HU") ~ "Hungary",
                                   COUNTRY_CODE %in% c("IE") ~ "Ireland",
                                   COUNTRY_CODE %in% c("LV") ~ "Latvia",
                                   COUNTRY_CODE %in% c("LU") ~ "Luxembourg",
                                   COUNTRY_CODE %in% c("MT") ~ "Malta",
                                   COUNTRY_CODE %in% c("PL") ~ "Poland",
                                   COUNTRY_CODE %in% c("PT") ~ "Portugal",
                                   COUNTRY_CODE %in% c("RO") ~ "Romania",
                                   COUNTRY_CODE %in% c("SK") ~ "Slovakia",
                                   COUNTRY_CODE %in% c("SI") ~ "Slovenia")) %>%
  group_by(COUNTRY_CODE, SEX, AGE, total_cases, total_pop) %>%
  filter(total_cases > 100) %>%
  mutate('age_cat_pct' = round((age_category_count/total_pop*100),digits = 2)) %>%
  select(COUNTRY_CODE, SEX, AGE, total_cases, total_pop, age_cat_pct) %>%
  group_by(COUNTRY_CODE, AGE, total_cases) %>%
  summarise(age_cat_pct = sum(age_cat_pct)) %>%
  arrange(desc(AGE))
```

```{r, echo=FALSE}

@@

@@

# Discussion
